|

### 2021-08-16 appendix/appendix.Rmd
Organizing folder

\begin{figure}[htb!]
  \begin{center}
  \begin{minipage}{1 \linewidth}
  \centerline{\includegraphics[width=5in,angle=0]{figs/McCrary.pdf}}
  \caption{\citet{McCrary2008} manipulation test}
  \bigskip
  \label{manipulationplot}
  \end{minipage}
  \end{center}
\end{figure}

@@

To provide an overview of the data dispersion, Figure \ref{sample_plot} plots the municipalities by their proximity from the cutoffs. In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds. The darker the color, the closer to the population thresholds. In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation. Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=7in,angle=0]{figs/samplePlot.pdf}}
      \caption{Municipalities by their Selection Status}
      \bigskip
      \label{sampleplot}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{0.9\linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{figs/simdistrRDD.pdf}}
      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
      \bigskip
      \label{simRDdd}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=4.5in,angle=0]{figs/estimsRDD.pdf}}
      \caption{Estimations for the Different Data Generating Processes}
      \bigskip
      \label{estimDGP}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{figs/bwSens.pdf}}
      \caption{Bandwidth Sensitivity -- Main Models}
      \bigskip
      \label{graphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{figs/placBwSens.pdf}}
      \caption{Placebo Regressions -- Bandwidth Sensitivity}
      \bigskip
      \label{placgraphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
      \bigskip
      \label{graphsensstatedrop1}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{figs/dropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
      \bigskip
      \label{graphsensstatedrop2}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=5in,angle=0]{figs/placDropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
      \bigskip
      \label{placgraphsensstatedrop1}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{figs/placDropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
      \bigskip
      \label{placgraphsensstatedrop2}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{figs/ffSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form}
      \bigskip
      \label{graphsensff}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{figs/placFfSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
      \bigskip
      \label{placgraphsensff}
  \end{center}
\end{figure}

@@

\begin{landscape}
\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=6in,angle=0]{figs/sensCov.pdf}}
      \caption{Sensitivity Analysis for the Control Variable's Choices}
\bigskip
\label{graphsenscontrol}
\end{minipage}
\end{center}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{figs/placSens1Cov.pdf}}
\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
\bigskip
\label{placsenscov1}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{figs/placSens2Cov.pdf}}
\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
\bigskip
\label{placsenscov2}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
\bigskip
\label{senscut1}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{figs/rdAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
\bigskip
\label{senscut2}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
\bigskip
\label{placsenscut1}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{figs/placRDAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
\bigskip
\label{placsenscut2}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{figs/distrRespSurvey.pdf}}
      \caption{Geographical Distribution of Survey Responses}
      \bigskip
      \label{geodistrsurv}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6.5in,angle=0]{figs/commonJobsCouncilors.pdf}}
      \caption{City Councilor's Common Activities}
\bigskip
\label{commonservice}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{1 \linewidth}
\centerline{\includegraphics[width=6.5in,angle=0]{figs/strategySupportMayors.pdf}}
\caption{Mayor negotiated services in exchange of support}
\bigskip
\label{mayorneg}
\end{minipage}
\end{center}
\end{figure}

>>>>

\begin{figure}[htb!]
  \begin{center}
  \begin{minipage}{1 \linewidth}
  \centerline{\includegraphics[width=5in,angle=0]{../figures/McCrary.pdf}}
  \caption{\citet{McCrary2008} manipulation test}
  \bigskip
  \label{manipulationplot}
  \end{minipage}
  \end{center}
\end{figure}

@@

To provide an overview of the data dispersion, Figure \ref{sampleplot} plots the municipalities by their proximity from the cutoffs. In the map we provide the contour of every Brazilian municipality, coloring it by the proximity to the council size thresholds. The darker the color, the closer to the population thresholds. In regression discontinuity, the closer a municipality is to the cutoff, the more influential it is in the estimation. Figure \ref{sampleplot} also shows that our municipalities are reasonably distributed around the whole country.

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=7in,angle=0]{../figures/samplePlot.pdf}}
      \caption{Municipalities by their Selection Status}
      \bigskip
      \label{sampleplot}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{0.9\linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/simdistrRDD.pdf}}
      \caption{Simulation RD with Multiple Thresholds -- Data Distribution}
      \bigskip
      \label{simRDdd}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=4.5in,angle=0]{../figures/estimsRDD.pdf}}
      \caption{Estimations for the Different Data Generating Processes}
      \bigskip
      \label{estimDGP}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/bwSens.pdf}}
      \caption{Bandwidth Sensitivity -- Main Models}
      \bigskip
      \label{graphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/placBwSens.pdf}}
      \caption{Placebo Regressions -- Bandwidth Sensitivity}
      \bigskip
      \label{placgraphbw}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Welfare Outcomes}
      \bigskip
      \label{graphsensstatedrop1}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/dropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Sample -- Mechanism Outcomes}
      \bigskip
      \label{graphsensstatedrop2}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=5in,angle=0]{../figures/placDropStateSens1.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Welfare Outcomes}
      \bigskip
      \label{placgraphsensstatedrop1}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/placDropStateSens2.pdf}}
      \caption{Sensitivity Analysis for the States in the Placebo Cutoffs -- Mechanism Outcomes}
      \bigskip
      \label{placgraphsensstatedrop2}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=8in,angle=0]{../figures/ffSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form}
      \bigskip
      \label{graphsensff}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/placFfSens.pdf}}
      \caption{Sensitivity Analysis for the Functional Form -- Placebo Cutoffs}
      \bigskip
      \label{placgraphsensff}
  \end{center}
\end{figure}

@@

\begin{landscape}
\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{\linewidth}
      \centerline{\includegraphics[height=6in,angle=0]{../figures/sensCov.pdf}}
      \caption{Sensitivity Analysis for the Control Variable's Choices}
\bigskip
\label{graphsenscontrol}
\end{minipage}
\end{center}
\end{figure}
\end{landscape}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens1Cov.pdf}}
\caption{Placebo Regressions Outcomes -- Sensitivity to Covariates}
\bigskip
\label{placsenscov1}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=5in,angle=0]{../figures/placSens2Cov.pdf}}
\caption{Placebo Regressions Mechanisms -- Sensitivity to Covariates}
\bigskip
\label{placsenscov2}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Welfare Outcomes}
\bigskip
\label{senscut1}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\centerline{\includegraphics[width=6in,angle=0]{../figures/rdAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Mechanism Outcomes}
\bigskip
\label{senscut2}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts1.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Welfare Outcomes}
\bigskip
\label{placsenscut1}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{0.8 \linewidth}
\centerline{\includegraphics[width=5.5in,angle=0]{../figures/placRDAddCuts2.pdf}}
\caption{Sensitivity to Addition of Cutoffs -- Placebo Mechanism Outcomes}
\bigskip
\label{placsenscut2}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6in,angle=0]{../figures/distrRespSurvey.pdf}}
      \caption{Geographical Distribution of Survey Responses}
      \bigskip
      \label{geodistrsurv}
    \end{minipage}
  \end{center}
\end{figure}

@@

\begin{figure}[htb!]
  \begin{center}
    \begin{minipage}{1 \linewidth}
      \centerline{\includegraphics[width=6.5in,angle=0]{../figures/commonJobsCouncilors.pdf}}
      \caption{City Councilor's Common Activities}
\bigskip
\label{commonservice}
\end{minipage}
\end{center}
\end{figure}

@@

\begin{figure}[htb!]
\begin{center}
\begin{minipage}{1 \linewidth}
\centerline{\includegraphics[width=6.5in,angle=0]{../figures/strategySupportMayors.pdf}}
\caption{Mayor negotiated services in exchange of support}
\bigskip
\label{mayorneg}
\end{minipage}
\end{center}
\end{figure}
